Trends in the contribution of major causes of death to the black-white life expectancy gap by US state

### 2018-05-11 Manuscript/Manuscript_COD_Trends_HealthandPlace.Rmd
format rmd

---
title: Trends in the contribution of major causes of death to the black-white life expectancy gap by US state
output:
  word_document: default
  html_document: default
always_allow_html: yes
---

@@

@@

----

@@

###Footnotes

>>>>

---
title: Trends in the contribution of major causes of death to the black-white life expectancy gap by US state
output: 
  word_document:
      reference_docx: reference.docx
---

@@

##### PAGE BREAK

@@

##### PAGE BREAK

@@
